Characterizing subarctic biomes for land surface modeling of pollution and climate risk.

### 2021-02-08 VegOzone.tex
Note about moving parts of section.

{\bf TODO: Move to Section~\ref{sec:do3se}.}
The opening of stomata, quantified through their conductance to water vapor $g_\mathrm{sto}$, is governed by different environmental factors and can be described by a multiplicative ansatz \citep{PTRS:Jarvis1976,ICP:MappingManual2017}:
\begin{equation}
  g^k_\text{sto, m} = g^k_\text{max, m} \cdot f^k_\text{phen} \cdot f^k_\text{light} \cdot \max{\left\{f^k_\text{min}, f^k_T \cdot f^k_D \cdot f^k_\text{SW}\right\}}.
  \label{eq:stomatal}
\end{equation}
%
The factors herein are normalized and vary within a range $0-1$. They are empirically determined and account for leaf phenology ($f_\text{phen}$), light ($f_\text{light}$), temperature ($f_T$), water vapor pressure deficit ($f_D$), and soil water content ($f_\text{SW}$). All factors differ with plant functional type (PFT) $k$.

>>>>

{\bf TODO: Move to Section~\ref{sec:do3se}.}
The opening of stomata is governed by different environmental factors and can be described by a multiplicative model \citep{PTRS:Jarvis1976,ICP:MappingManual2017}:
\begin{equation}
  g^k_\text{sto, m} = g^k_\text{max, m} \cdot f^k_\text{phen} \cdot f^k_\text{light} \cdot \max{\left\{f^k_\text{min}, f^k_T \cdot f^k_D \cdot f^k_\text{SW}\right\}}.
  \label{eq:stomatal}
\end{equation}
%
The factors herein are normalized and vary within a range $0-1$. They are empirically determined and account for leaf phenology ($f_\text{phen}$), light ($f_\text{light}$), temperature ($f_T$), water vapor pressure deficit ($f_D$), and soil water content ($f_\text{SW}$). All factors differ with plant functional type (PFT) $k$.
